Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-12 paper/main.tex
cleaning before printing

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
% localizer substitute
[An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.]
\end{abstract}

@@

\begin{itemize}
    \item speaking of "primary contrast" probably not necessary anymore.
    \item main text: add references to supplemental material
\end{itemize}

@@

\begin{itemize}
    \item Fig regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
\end{itemize}

@@

\begin{itemize}
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

\end{itemize}

\noindent Discussion
\begin{itemize}
    \item summary \& overall conclusion (last paragraph or independent section)
\end{itemize}

@@

\todo[inline]{~1000 words}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with differrent semantic
categories occurring in spoken language.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.
% Aziz' tasks:
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
jaw'')
% Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

\todo[inline]{~3500 words}

@@

% traditionally
Traditionally, researchers specifically design stimuli that presumably would
trigger the perceptual process of interest while also controlling confounding
variables (e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated a the temporal structure of a various stimulus features that
later served as a basis (for GLM regressors) to model hemodynamic responses.

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{better focus on cinematographic rationale \& drop last sentence; activity
in e.g. FFA adopts too -> we might substract an on average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\section{Results}
\todo[inline]{800 words}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts withn a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\todo[inline]{1700 words}
% Discussion: explains how results fill gap identified in intro

@@

\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
whole-brain analysies, so probably ``localization'', }

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via general
linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentially
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

\subsection{PPA group}

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
categorized each frame after a cut independent of its specific content.
\todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas should extensively annotate the content of frames (e.g.
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinamtography
We here took advantage of an idiosncracy of movie directing to shift from
establishing the geometry earlier in the movie to later depicting persons and
objects more relevant to the evolved plot.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in a audio-visual movie.

@@

\subsection{PPA individuals (AD)}

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
%
We examined the results from the audio-description's primary contrast on an
individual level to test if an auditory narrative could [in principle]
substitute a visual localizer experiment.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used one contrast and a ``one threshold fits all approach`` (Z>3.4,
p<.05 cluster-corrected).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but the same pattern can can reliably be
found in individual study participants.
% concluding statement
our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

\todo[inline]{probably not important but: what do results suggest
regarding individual differences?  Differences in alertness, attention to
spatial information, predisposition?  ``capability'' to process auditory spatial
information?}

% question

\subsection{PPA individuals (AD)}

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed activation pattern could be attributed to be attributed to
different features inherent in visual compared to verbal stimuli.\todo{ouff}
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than the pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

\subsection{RSC \& LOC = non random clusters => naturalistic stimuli are
cool}

% no random clusters
Despite performing a whole brain analysis, we do not find clusters in the
primary contrast or across contrasts (s. supplemental material) that hamper the
interpretation of results.
% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).

\todo[inline]{AD clusters in LOC are more medial in AD stimulus compared to AV;
whereas clusters in PPA and RSC of both stimuli overlap}
% conclusion
\todo[inline]{concluding statement??}

This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration) depend on the extent to which the multi-dimensionality
of the naturalistic stimulus is annotated, modeled, statistically controlled and
/ or how many events the stimulus provides per assumed perceptual process for
the averaging purpose

\section{summary}

\todo[inline]{join summary \& conclusion}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
% localizer substitute
[An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.]
\end{abstract}

@@

\begin{itemize}
    \item main text: add references to supplemental material
\end{itemize}

@@

\begin{itemize}
    \item Fig regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
    \item different frame counts of segments AV vs. AD
\end{itemize}

@@

\begin{itemize}
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
        PPA". Machst wohl das erste, beschreibst es aber als das zweite
    \item Summary / Concluding statement
        (data reuse to present compelling new findings \& conclusions derived
        from published.)
\end{itemize}

\noindent Supplemental Material
\begin{itemize}
    \item restructure (results + discussion AV, then AD)
    \item discuss differences of contrasts (s. Simons comment)
\end{itemize}

\noindent Code Availability
\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
\end{itemize}

\noindent Data Availability
\begin{itemize}
    \item s. other psyinfo paper
\end{itemize}

@@

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with different semantic
categories occurring in spoken language.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.
% Aziz' tasks:
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
jaw'')
% Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

@@

% traditionally
Traditionally, researchers specifically design stimuli that presumably would
trigger the perceptual process of interest while also controlling confounding
variables (e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of a various stimulus features that
later served as a basis (for GLM regressors) to model hemodynamic responses.

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{drop last sentence \& better focus on cinematographic rationale; activity
in e.g. FFA adopts too -> we might subtract an on average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\section{Results}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (see Table
\ref{tab:res-av-group1}, Figure \ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% Discussion: explains how results fill gap identified in intro

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via general
linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

\subsection{PPA (group + individuals \& aPPA vs. pPPA)}

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
categorized each frame after a cut independent of its specific content.
\todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas should extensively annotate the content of frames (e.g.
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
establishing the geometry earlier in the movie to later depicting persons and
objects more relevant to the evolved plot.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in a audio-visual movie.

@@

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in an unthresholded $t$-map from one of three contrasts by visual
judgment, we used the same contrast and threshold (Z>3.4, p<.05
cluster-corrected) for all subjects.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 subjects
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

\todo[inline]{discussion of Bland-Altman-Plots?; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that process specific apsects of a visual scene and
cooperate to build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as inherent in both visual and
verbal stimuli.

\subsection{RSC \& LOC; naturalistic stimuli}

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides
and to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

\section{conclusion}
